Analysis of Odd one out experiment

### 2019-06-05 reports/odd_one_out/analysis_oddoneout.Rmd
additional changes
- move compute duration into markdown file
- fix get dur function
- add random slopes to the model

```{r create plot dir}
plots_dir <- here::here("plots", "oddoneout")

@@

@@

glm1 <- glmer(cbind(correct,1-correct) ~ quintile + (1|subject_id) + (1|category), df, family = binomial())
glm1_null <- glmer(cbind(correct,1-correct) ~ (1|subject_id) + (1|category), df, family = binomial())
anova(glm1, glm1_null)

@@

glm2 <- glmer(cbind(correct,1-correct) ~ d_ratio + (1|subject_id) + (1|category), df, family = binomial())
glm2_null <- glmer(cbind(correct,1-correct) ~ (1|subject_id) + (1|category), df, family = binomial())
anova(glm2, glm2_null)

>>>>

```{r create plot dir}
plots_dir <- here("plots", "oddoneout")

@@

# Duration of the exp

```{r duration of the exp}
data_pth <- here("data", "oddoneout", "results_categ")

exp_duration <- data_pth %>% 
  dir(pattern = "*.log", full.names = T) %>% 
  purrr::map(read_file) %>% 
  purrr::map_dbl(get_dur)

Average experiment duration: `r (exp_duration / 60) %>% mean() %>% round(2)`, SD = `r (exp_duration / 60) %>% sd() %>% round(2)`

@@

glm1 <- glmer(correct ~ quintile + (1+quintile|subject_id) + (1+quintile|category), df, family = binomial())
glm1_null <- glmer(correct ~ (1+quintile|subject_id) + (1+quintile|category), df, family = binomial())
anova(glm1, glm1_null)

@@

glm2 <- glmer(correct ~ d_ratio + (1+d_ratio|subject_id) + (1+d_ratio|category), df, family = binomial())
glm2_null <- glmer(correct ~ (1+d_ratio|subject_id) + (1+d_ratio|category), df, family = binomial())
anova(glm2, glm2_null)
